[Re] A neural model of the saccade generator in the reticular formation

### 2018-04-24 article/senden-schuecker-hahne-diesmann-goebel-2018.tex
corrected index sequence & forward Euler -> Forward Euler

The SG model described by Gancarz \& Grossberg \autocite{Gancarz1998}
consists of a horizontal and a vertical component each with two
long-lead burst neurons (LLBNs), excitatory burst neurons (EBNs),
inhibitory burst neurons (IBNs), and tonic neurons (TNs). Within each
component, the two directions (left-right, down-up) interact
antagonistically. Additionally, both components share a single omnipause
neuron (OPN) which tonically inhibits each EBN to suppress unwanted
saccades. While this constitutes the core SG model, the superior
colliculus (SC) is relevant for some simulations. In what follows we
briefly describe the dynamics of neurons within the horizontal component
(equivalent descriptions apply to the vertical component). Please note
that subscripts \(\mathrm{l}\), \(\mathrm{r}\), \(\mathrm{d}\) and
\(\mathrm{u}\) indicate whether a neuron controls upward, downward,
leftward or rightward saccade direction, respectively.

@@

In all simulations we use the Exponential Euler (EE) method for
numerical integration of all except tonic neurons \autocite{Hahne2017}
at a time step of \(0.05\,\mathrm{ms}\) and a time constant of
\(50\,\mathrm{ms}\). Tonic neurons are integrated using the forward
Euler method since they do not exhibit passive decay leading to
division-by-zero when using the EE method. It should be noted that the
initial firing rates of neurons are not in equilibrium. In order to
address this, the model evolves for \(100\,\mathrm{ms}\) to relax
towards equilibrium before any input is applied. Furthermore, as in the
original publication, any activity is bounded from below at zero.
Finally, we always simulate the full model; i.e.~both its horizontal and
vertical components even if input is applied only to one of the two.

>>>>

The SG model described by Gancarz \& Grossberg \autocite{Gancarz1998}
consists of a horizontal and a vertical component each with two
long-lead burst neurons (LLBNs), excitatory burst neurons (EBNs),
inhibitory burst neurons (IBNs), and tonic neurons (TNs). Within each
component, the two directions (left-right, down-up) interact
antagonistically. Additionally, both components share a single omnipause
neuron (OPN) which tonically inhibits each EBN to suppress unwanted
saccades. While this constitutes the core SG model, the superior
colliculus (SC) is relevant for some simulations. In what follows we
briefly describe the dynamics of neurons within the horizontal component
(equivalent descriptions apply to the vertical component). Please note
that subscripts \(\mathrm{u}\), \(\mathrm{d}\), \(\mathrm{l}\) and
\(\mathrm{r}\) indicate whether a neuron controls upward, downward,
leftward or rightward saccade direction, respectively.

@@

In all simulations we use the Exponential Euler (EE) method for
numerical integration of all except tonic neurons \autocite{Hahne2017}
at a time step of \(0.05\,\mathrm{ms}\) and a time constant of
\(50\,\mathrm{ms}\). Tonic neurons are integrated using the Forward
Euler method since they do not exhibit passive decay leading to
division-by-zero when using the EE method. It should be noted that the
initial firing rates of neurons are not in equilibrium. In order to
address this, the model evolves for \(100\,\mathrm{ms}\) to relax
towards equilibrium before any input is applied. Furthermore, as in the
original publication, any activity is bounded from below at zero.
Finally, we always simulate the full model; i.e.~both its horizontal and
vertical components even if input is applied only to one of the two.
